Implementation of a stable, high-power optical lattice for quantum gas microscopy

### 2019-01-29 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
Updated referee comments

Although it is an essential part of the system, the loop filter is also one of its major limitations. Figure~\ref{fig:noises} shows the noise performance of the output of the fiber amplifiers in open-loop compared to the noise in closed-loop.
Noise near DC is lowered (as expected from a closed-loop system), noise outside the loop bandwidth is increased in the range of 10 to \unit{450}{kHz} as seen in subfigures (c) and (d).
This can be explained by the Johnson noise~\cite{Horowitz2015} on the \unit{1}{k\Omega} op-amp input resistors, amplified by the amplification stages of the loop filter.
The sharp drop off at the \unit{450}{kHz} point is due to a low-pass filter placed on the output of the loop filter, far above the maximum bandwidth set by the AOM.
When the broadband noise below \unit{450}{kHz} was determined to be a problem, we decided that a bandwidth of higher than \unit{10}{kHz} was not required in the foreseeable future.
As a result, we added a first-order low pass with a \unit{3}{dB} frequency of \unit{10}{kHz} leading to the improvement shown in Fig.~\ref{fig:low_pass_noises}. The fiber amplifier used to take this data was different from the one used for Fig.~\ref{fig:noises}, although their performance is comparable.

>>>>

Although it is an essential part of the system, the loop filter is also one of its major limitations. Figure~\ref{fig:noises} shows the noise performance of the output of the fiber amplifiers in open-loop compared to the noise in closed-loop.
Noise near DC is lowered (as expected from a closed-loop system), noise outside the loop bandwidth is increased in the range of 10 to \unit{450}{kHz} as seen in subfigures (c) and (d).
This can be explained by the noise gain of the op-amp circuits in combination with the speed limitations of the nonlinear output stage~\cite{Horowitz2015}.
The sharp drop off at the \unit{450}{kHz} point is due to a low-pass filter placed on the output of the loop filter, far above the maximum bandwidth set by the AOM.
When the broadband noise below \unit{450}{kHz} was determined to be a problem, we decided that a bandwidth of higher than \unit{10}{kHz} was not required in the foreseeable future.
As a result, we added a first-order low pass with a \unit{3}{dB} frequency of \unit{10}{kHz} leading to the improvement shown in Fig.~\ref{fig:low_pass_noises}. The fiber amplifier used to take this data was different from the one used for Fig.~\ref{fig:noises}, although their performance is comparable.
